The \vspec{} Collection: A suite of utilities to model spectroscopic phase curves of 3D exoplanet atmospheres in the presence of stellar variability.

### 2024-09-26 src/tex/ms.tex
[reviewer] add language about discontinuity at the poles

The treatment by \citet{cowan2011} includes no mixing in the latitudinal direction, nor a vertical temperature profile. To allow for variations in pressure and inclination, we augment their treatment with several simple approximations for latitudinal and vertical temperature variations.

>>>>

The treatment by \citet{cowan2011} includes no mixing in the latitudinal direction, nor a vertical temperature profile. To allow for variations in pressure and inclination, we augment their treatment with several simple approximations for latitudinal and vertical temperature variations. However, it should be noted that these assumptions produce a discontinuity at the poles, which is non-physical. A more physically-motivated model of latitudinal mixing (e.g., including a diffusion parameter in the heat transport equation) would avoid this caveat, but would also be more expensive to produce.
